Game-theoretic strengthenings of Menger's property

### 2014-07-17 phd/talks-and-presentations/2014-07-23-menger-talk.tex
incorporate feedback from G

\section{Introduction}

\subsection{Abstract}

\begin{frame}{Abstract}%{Subtitles are optional.}
    \small
    A certain topological game introduced by Hurewicz characterizes Menger's
    covering property whenever the first player lacks a winning strategy. It
    was later shown by Telgarsky (and later by Scheepers using a different
    argument) that for metric spaces, the second player having a winning
    strategy characterizes the stronger property of $\sigma$-compactness.

    \vspace{1em}

    We factor out Scheepers' proof to show
    that for regular spaces, the second player having a winning $1$-Mark\"ov
    strategy characterizes $\sigma$-compactness; also, for second-countable
    spaces, the presence of a winning perfect information strategy for the
    second player implies the existence of a winning $1$-Mark\"ov strategy for
    that player. We also show the that for all $k$, the existence of a
    winning $k$-Mark\"ov strategy for the second player implies the existence
    of a winning $2$-Mark\"ov strategy, and give a space which permits
    a winning $2$-Mark\"ov strategy but not a winning $1$-Mark\"ov strategy.
\end{frame}

@@

  \begin{definition}
    Let $\fillgameInt\kappa$ denote the \term{intersection filling game}
    analogous to $\fillgameS\kappa$, except that $\pl C$ has no restriction
    on the countable sets she choooses, but $\pl F$ need only ensure that
    $\bigcup_{n<\omega}\mc F_n\supseteq \bigcap_{n<\omega}\mc U_n$ to win
    the game.
  \end{definition}
\end{frame}

@@

  Any sufficient property must imply $\pl F\win\mengame X$ (ruling out
  Hurewicz[?]), and any (interesting) necessary property shouldn't be implied by
  $\pl F\win\mengame X$ (ruling out Alster and productively Lindel\"of for
  regular spaces).
\end{frame}

>>>>

% \section{Introduction}

% \subsection{Abstract}

% \begin{frame}{Abstract}%{Subtitles are optional.}
%     \small
%     A certain topological game introduced by Hurewicz characterizes Menger's
%     covering property whenever the first player lacks a winning strategy. It
%     was later shown by Telgarsky (and later by Scheepers using a different
%     argument) that for metric spaces, the second player having a winning
%     strategy characterizes the stronger property of $\sigma$-compactness.

%     \vspace{1em}

%     We factor out Scheepers' proof to show
%     that for regular spaces, the second player having a winning $1$-Mark\"ov
%     strategy characterizes $\sigma$-compactness; also, for second-countable
%     spaces, the presence of a winning perfect information strategy for the
%     second player implies the existence of a winning $1$-Mark\"ov strategy for
%     that player. We also show the that for all $k$, the existence of a
%     winning $k$-Mark\"ov strategy for the second player implies the existence
%     of a winning $2$-Mark\"ov strategy, and give a space which permits
%     a winning $2$-Mark\"ov strategy but not a winning $1$-Mark\"ov strategy.
% \end{frame}

@@

  \begin{definition}
    Let $\fillgameInt\kappa$ denote the \term{intersection filling game}
    analogous to $\fillgameS\kappa$, except that $\pl C$ has no restriction
    on the countable sets she choooses, but $\pl F$ need only ensure that
    $\bigcup_{n<\omega} F_n\supseteq \bigcap_{n<\omega} C_n$ to win
    the game.
  \end{definition}
\end{frame}

@@

  Any sufficient property would imply $\pl F\win\mengame X$, and any
  (interesting) necessary property shouldn't be implied by
  $\pl F\win\mengame X$. Assuming $T_3$, properties which come to mind
  from the literature fit the latter: e.g. Alster (Aurichi, Tall 2013),
  and thus productively Lindel\"of (Alster 1988) and Hurewicz (Tall 2009).
\end{frame}
